Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 ms.tex
colorful

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
    galaxies in our sample as a function of the stellar wind heating
    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.
    Green, orange, and blue symbols correspond to different values of
    $v_{w} =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
    correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
    correspond to cores ($\Gamma = 0.1$). Green crosses correspond to
    cusp solutions which would be thermally unstable. The black curves
    correspond to the analytic prediction from equation
    (\ref{eq:rs2main}), with solid and dashed curves calculated for
    parameters $(\Gamma=0.8, \densSlope\simeq1)$ and
    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. }
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green crosses correspond to cusp solutions which
    would be thermally unstable.  Solid and dashed curves correspond
    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively. }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average SFHs from
  \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for
  details).  {\it Middle Panel:} The ratio of the total heating rate
  ($\dot{q}_{\rm heat} \propto v_{w}^{2}$) from the top panel to the
  radiating cooling rate ($|\dot{q}_{\rm rad}|$) at the stagnation
  radius. {\it Bottom panel} Parameter $\eta$ characterizing stellar
  mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star SFHs from \citealt{MosterNaab+:2013a} and the
  ratio of Ia radius to stagnation radius as a function of $\Mbh$.}
  %The Ia radius calculated from equation~\eqref{eq:rIa} based on
  %convolving the average star formation histories with the SN Ia DTD.
  %The stagnation radius is calculated from \eqref{eq:stag_simple}
  %using the total heating rate for each $\Mbh$ shown in the top panel
  %assuming a cusp galaxy ($\Gamma=0.8$).}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} Stagnation radius $r_{s}$ in units of the
    sphere of influence radius $r_{\rm inf}$ (eq.~[\ref{eq:rsoi}]) for
    galaxies in our sample as a function of the stellar wind heating
    parameter $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^{2}}$.
    Green, orange, and blue symbols correspond to different values of
    $v_{w} =$ 300, 600, and 1200 km s$^{-1}$, respectively.  Squares
    correspond to cusp galaxies ($\Gamma = 0.8$), while triangles
    correspond to cores ($\Gamma = 0.1$). Green circles correspond to
    cusp solutions which would be thermally unstable. The black curves
    correspond to the analytic prediction from equation
    (\ref{eq:rs2main}), with solid and dashed curves calculated for
    parameters $(\Gamma=0.8, \densSlope\simeq1)$ and
    $(\Gamma=0.1,\densSlope\simeq0.6)$, respectively. }
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green circles correspond to cusp solutions which
    would be thermally unstable.  Solid and dashed curves correspond
    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively. }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSources.pdf}
\caption{\label{fig:vwSources} {\it Top Panel:} Sources contributing
  to the total heating rate of the CNM, $\vwO$ ({\it black}),
  including stellar wind heating ({\it orange}), Ia supernovae ({\it
    green}), millisecond pulsars ({\it blue}), and compton heating
  ({\it pink}).  Each heating source varies with black hole mass
  $\Mbh$ calculated for average SFHs from \citet{MosterNaab+:2013a}
  (see Appendix~\ref{app:windheat} for details).  {\it Bottom Panel:}
  The ratio of the total heating rate ($\dot{q}_{\rm heat} \propto
  v_{w}^{2}$) from the top panel to the radiative cooling rate
  ($|\dot{q}_{\rm rad}|$) at the stagnation radius (red), parameter $\eta$
  characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a
  function of black hole mass $\Mbh$, calculated for average star SFHs
  from \citealt{MosterNaab+:2013a} (blue) and the ratio of Ia radius to
  stagnation radius as a function of $\Mbh$ (green).}
\end{figure}
